### 2016-08-17 architecture.tex
Move footnotes to the right of punctuation

In SymPy every symbolic expression is an instance of a Python \texttt{Basic}
class\footnote{Some
  internal classes, such as those used in the polynomial module, do not follow
  this rule for efficiency reasons.}, a superclass of all SymPy types providing
common methods to all SymPy tree-elements, such as traversals.  The children of a node in the
tree are held in the \texttt{args} attribute.  A terminal or leaf node in the
expression tree has empty \texttt{args}.

@@

Some of the common assumptions that SymPy allows are \texttt{positive},
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}\footnote{SymPy assumes that two
  expressions $A$ and $B$ commute with each other multiplicatively, that is,
  $A\cdot B=B\cdot A$, unless they both have \texttt{commutative=False}. Many
  algorithms in SymPy require special consideration to work correctly with
  noncommutative products.}. Assumptions on any object can be checked with the
\verb|is_|\texttt{\textit{assumption}} attributes, like \verb|t.is_positive|.

>>>>

In SymPy every symbolic expression is an instance of a Python \texttt{Basic}
class,\footnote{Some
  internal classes, such as those used in the polynomial module, do not follow
  this rule for efficiency reasons.} a superclass of all SymPy types providing
common methods to all SymPy tree-elements, such as traversals.  The children of a node in the
tree are held in the \texttt{args} attribute.  A terminal or leaf node in the
expression tree has empty \texttt{args}.

@@

Some of the common assumptions that SymPy allows are \texttt{positive},
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}.\footnote{SymPy assumes that two
  expressions $A$ and $B$ commute with each other multiplicatively, that is,
  $A\cdot B=B\cdot A$, unless they both have \texttt{commutative=False}. Many
  algorithms in SymPy require special consideration to work correctly with
  noncommutative products.} Assumptions on any object can be checked with the
\verb|is_|\texttt{\textit{assumption}} attributes, like \verb|t.is_positive|.

### 2016-08-17 gruntz.tex
Move footnotes to the right of punctuation

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:

>>>>

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:\footnote{To see intermediate steps, discussed above, interested
readers can switch on debugging output by setting
the environment variable \texttt{SYMPY\_DEBUG=True}, before importing anything from
the SymPy namespace.}

### 2016-08-17 introduction.tex
Move footnotes to the right of punctuation

The following statement imports all SymPy functions into the global Python
namespace.\footnote{\texttt{import *} has been used here to aid the
  readability of the paper, but is best to avoid such wildcard import
  statements in production code, as they make it unclear which names are
  present in the namespace. Furthermore, imported names could clash with
  already existing imports from another package. For example, SymPy, the
  standard Python \texttt{math} library, and NumPy all define the \texttt{exp}
  function, but only the SymPy one will work with SymPy symbolic expressions.}
From here on, all examples in this paper assume that this statement has been
executed\footnote{Three greater-than signs denote standard
Python prompt for interactive session.}:

>>>>

The following statement imports all SymPy functions into the global Python
namespace.\footnote{\texttt{import *} has been used here to aid the
  readability of the paper, but is best to avoid such wildcard import
  statements in production code, as they make it unclear which names are
  present in the namespace. Furthermore, imported names could clash with
  already existing imports from another package. For example, SymPy, the
  standard Python \texttt{math} library, and NumPy all define the \texttt{exp}
  function, but only the SymPy one will work with SymPy symbolic expressions.}
From here on, all examples in this paper assume that this statement has been
executed:\footnote{Three greater-than signs denote standard
Python prompt for interactive session.}
